### 2019-12-27 README.Rmd
clarify "developmental" language

To install the developmental version of `infer`, make sure to install `remotes` first. The `pkgdown` website for this version is at <https://infer.netlify.com>.

@@

To install the cutting edge version of `infer` (do so at your own risk), make sure to install `remotes` first.

@@

To see documentation for the developmental version of `infer`, the developmental `pkgdown` site is available at <https://infer-dev.netlify.com>.

>>>>

To install the developmental stable version of `infer`, make sure to install `remotes` first. The `pkgdown` website for this version is at <https://infer.netlify.com>.

@@

To install the experimental version of `infer` (do so at your own risk), make sure to install `remotes` first.

@@

To see documentation for the experimental version of `infer`, the `pkgdown` site is available at <https://infer-dev.netlify.com>.
